%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Newton, Iperdesign Srl} % Organization
    {Rome, Italy} % Location
    {Sept. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analysis of customer needs and participation in defining the technical and functional specifications of projects.}
        \item {Design and development of web and mobile applications according to customer requirements.}
        \item {Designing modular, scalable,and secure software architectures for our applications}
        \item {Design, development, and management of relational and non-relational databases for our applications}
        \item {Integration of third-party APIs and external services into developed software solutions.}
        \item {Integration and use of cloud services for our applications.}
        \item {Corrective and evolutionary maintenance of existing software.}
        \item {Writing technical documentation and implementing best practices in development.}
        \item {Optimize application performance and security.}
        \item {Collaborate with design and project management teams to ensure consistency between the user interface, customer experience, and application logic}
        \item {Participate in technical reviews and progress meetings with clients and the internal team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer programmer (Doctoral thesis project)} % Job title
    {Sorbonne University} % Organization
    {Paris, France} % Location
    {Feb. 2022 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Complete conversion and rewriting of scientific code originally written in Python to Rust, with improved performance and memory management.}
        \item {Collaboration with researchers and doctoral students to integrate the Rust version into the thesis framework.}
        \item {Setting up a testing and benchmarking environment.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
